Vaccines: Many Beliefs Pilot 5

### 2018-09-18 pilots/pilot4/vacc_manyBelief_pilot4.Rmd
added files

---
title: "Vaccines: Many Beliefs Pilot 3"
author: "Derek Powell"
date: "June 26, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

@@

filename <- "data/vb_pilot3.csv"

@@

df <- df[ , -which(names(df) %in% remove_cols)]
```

```{r}
all_items <- c("hb_hb_1",
"hb_hb_2",
"hb_hb_3",
"hb_hb_4",
"nat_nat_1",
"nat_nat_2r",
"nat_nat_3",
"nat_nat_4",
"nat_nat_5",
"medSkept_medSkept_1",
"medSkept_medSkept_2r",
"medSkept_medSkept_3",
"medSkept_medSkept_4",
"medSkept_medSkept_5",
"medSkept_medSkept_6",
"diseaseRare_diseaseRare_1",
"diseaseRare_diseaseRare_2",
"diseaseRare_diseaseRare_3",
"diseaseRare_diseaseRare_4",
"diseaseSevere_diseaseSevere_1",
"diseaseSevere_diseaseSevere_2",
"diseaseSevere_diseaseSevere_3",
"diseaseSevere_diseaseSevere_4r",
"diseaseSevere_diseaseSevere_5",
"diseaseSevere_diseaseSevere_6",
"vaccEff_vaccEff_1",
"vaccEff_vaccEff_2r",
"vaccEff_vaccEff_3r",
"vaccEff_vaccEff_4",
"vaccDanger_vaccDanger_1",
"vaccDanger_vaccDanger_2",
"vaccDanger_vaccDanger_3",
"vaccDanger_vaccDanger_4r",
"vaccTox_vaccTox_1",
"vaccTox_vaccTox_2",
"vaccTox_vaccTox_3",
"vaccTox_vaccTox_4r",
"vaccStrain_vaccStrain_1",
"vaccStrain_vaccStrain_2r",
"vaccStrain_vaccStrain_3",
"vaccStrain_vaccStrain_4",
"vaccStrain_vaccStrain_5",
"vaccIntent_vaccIntent_1r",
"vaccIntent_vaccIntent_2",
"vaccIntent_vaccIntent_3r",
"vaccIntent_vaccIntent_4",
"vaccIntent_vaccIntent_5r",
"parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",
"parentExpert_parentExpert_3",
"parentExpert_parentExpert_4r",
"infantImmLimCap_infantImmLimCap_1",
"infantImmLimCap_infantImmLimCap_2r",
"infantImmLimCap_infantImmLimCap_3",
"infantImmLimCap_infantImmLimCap_4",
"infantImmLimCap_infantImmLimCap_5",
"immSympt_immSympt_1",
"immSympt_immSympt_2r",
"immSympt_immSympt_3r",
"immSympt_immSympt_4",
"immSympt_immSympt_5r",
"immSympt_immSympt_6",
"immSympt_immSympt_7r",
"infantImmWeak_infantImmWeak_1",
"infantImmWeak_infantImmWeak_2",
"infantImmWeak_infantImmWeak_3",
"infantImmWeak_infantImmWeak_4r",
"overpar_overpar_1r",
"overpar_overpar_2r",
"overpar_overpar_3",
"overpar_overpar_4",
"overpar_overpar_5")

@@

```{r}
library(ggplot2)
# df <- read.csv("vb_pilot2.csv")
df <- df[which(df$diseaseRare_check_5==5),]

@@

This is a notebook for the first pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 6 to comprehension checks, leaving 94.

@@

Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters. Whereas we treated these as 15 different scales, this finds just 3 separate clusters. I don't think this is a problem--we expected and even hoped these scales would be correlated with one another.

@@

@@

@@

```{r}
hb <- c("hb_hb_1",
"hb_hb_2",
"hb_hb_3",
"hb_hb_4")

@@

```{r}
nat <- c("nat_nat_1",
"nat_nat_2r",
"nat_nat_3",
"nat_nat_4",
"nat_nat_5")

naturalism.alpha <- psych::alpha(df[,nat])
naturalism.alpha$total$raw_alpha

corrplot(cor(df[,nat]),
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

@@

**NOTE**: we previously scored this one kind of strangely, so it's now been relabeld as "diseaseRare" to indicate that it reflects participants' belief the diseases are extremely rare.

```{r}
diseaseRare <- c("diseaseRare_diseaseRare_1",
"diseaseRare_diseaseRare_2",
"diseaseRare_diseaseRare_3",
"diseaseRare_diseaseRare_4")

@@

Disease severe is now a highly reliable scale (and could even remove an item.)

```{r}
diseaseSevere <- c("diseaseSevere_diseaseSevere_1",
"diseaseSevere_diseaseSevere_2",
"diseaseSevere_diseaseSevere_3",
"diseaseSevere_diseaseSevere_4r",
"diseaseSevere_diseaseSevere_5",
"diseaseSevere_diseaseSevere_6")

```
### Diagnosing

Here are histograms of each item

ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
corrplot(cor(df[,diseaseSevere]),
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

@@

```{r}
vaccEff <- c("vaccEff_vaccEff_1",
"vaccEff_vaccEff_2r",
"vaccEff_vaccEff_3r",
"vaccEff_vaccEff_4")

@@

```{r}
vaccDanger <- c("vaccDanger_vaccDanger_1",
"vaccDanger_vaccDanger_2",
"vaccDanger_vaccDanger_3",
"vaccDanger_vaccDanger_4r")

@@

```{r}
vaccTox <- c("vaccTox_vaccTox_1",
"vaccTox_vaccTox_2",
"vaccTox_vaccTox_3",
"vaccTox_vaccTox_4r")

@@

```{r}
medSkept <- c("medSkept_medSkept_1",
"medSkept_medSkept_2r",
#"medSkept_medSkept_3", # planned to remove
"medSkept_medSkept_4",
"medSkept_medSkept_5",
"medSkept_medSkept_6")

medSkept.alpha <- psych::alpha(df[,medSkept])
medSkept.alpha$total$raw_alpha
medSkept.alpha
```

@@

```{r}
vaccIntent <- c("vaccIntent_vaccIntent_1r",
"vaccIntent_vaccIntent_2",
"vaccIntent_vaccIntent_3r",
"vaccIntent_vaccIntent_4",
"vaccIntent_vaccIntent_5r")

@@

Success!

```{r}
parExpert <- c("parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",
"parentExpert_parentExpert_3",
"parentExpert_parentExpert_4r")

parExpert.alpha <- psych::alpha(df[,parExpert])
parExpert.alpha$total$raw_alpha
parExpert.alpha
```
```{r}
library(ggplot2)
library(reshape2)

@@

Reliability is still weak Might improve if we ditch my new item #5

```{r}
immCap <- c(
  "infantImmLimCap_infantImmLimCap_1",
"infantImmLimCap_infantImmLimCap_2r",
"infantImmLimCap_infantImmLimCap_3",
"infantImmLimCap_infantImmLimCap_4",
"infantImmLimCap_infantImmLimCap_5")

@@

library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,immCap]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,immCap]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

## Immune system produces cold symptoms

Reliability actually got worse!

```{r}
immSympt <- c("immSympt_immSympt_1",
"immSympt_immSympt_2r",
"immSympt_immSympt_3r",
"immSympt_immSympt_4",
"immSympt_immSympt_5r",
"immSympt_immSympt_6",
"immSympt_immSympt_7r")

immSympt.alpha <- psych::alpha(df[,immSympt])
immSympt.alpha$total$raw_alpha
immSympt.alpha

No obvious fixes here -- just a mess.

```{r}
# library(ggplot2)
# library(reshape2)
# 
# ggplot(data = melt(df[,immSympt]), mapping = aes(x = value)) + 
#     geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
# 
# corrplot(cor(df[,immSympt]),
#          order="AOE",
#          tl.cex=.65,
#          tl.col="black",
#          method="color",
#          addCoef.col="black",
#          col=viridis(128))
```

# ggplot(data = melt(df[,immSympt]), mapping = aes(x = value)) + 
#     geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,c(immCap,immWeak)]),
         order="AOE",
         tl.cex=.5,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

@@

Looks pretty good.

```{r}
immWeak <- c("infantImmWeak_infantImmWeak_1",
"infantImmWeak_infantImmWeak_2",
"infantImmWeak_infantImmWeak_3",
"infantImmWeak_infantImmWeak_4r")

@@

```{r}
vaccStrain <- c("vaccStrain_vaccStrain_1",
"vaccStrain_vaccStrain_2r",
"vaccStrain_vaccStrain_3",
"vaccStrain_vaccStrain_4",
"vaccStrain_vaccStrain_5")

@@

This is a brand new scale so these numbers are ok but probably want this improved. Could be improved slightly by removing item #2.

```{r}
overPar <- c("overpar_overpar_1r",
"overpar_overpar_2r",
"overpar_overpar_3",
"overpar_overpar_4",
"overpar_overpar_5")

@@

```{r}
df_scales<-df_main
df_scales$holBalance <- rowMeans(df[,hb])
df_scales$naturalism <- rowMeans(df[,nat])
df_scales$diseaseRare <- rowMeans(df[,diseaseRare])
df_scales$diseaseSevere <- rowMeans(df[,diseaseSevere])
df_scales$vaccEff <- rowMeans(df[,vaccEff])
df_scales$vaccDanger <- rowMeans(df[,vaccDanger])
df_scales$medSkept <- rowMeans(df[,medSkept])
df_scales$vaccIntent <- rowMeans(df[,vaccIntent])
# df_scales$parDuty <- rowMeans(df[,parDuty])
df_scales$parExpert <- rowMeans(df[,parExpert])
df_scales$immCap <- rowMeans(df[,immCap])
df_scales$immSympt <- rowMeans(df[,immSympt])
df_scales$immWeak <- rowMeans(df[,immWeak])
df_scales$vaccStrain <- rowMeans(df[,vaccStrain])
df_scales$vaccTox <- rowMeans(df[,vaccTox])
df_scales$overParenting <- rowMeans(df[,overPar])
```

@@

scale_vars <- c("holBalance",
                "naturalism",
                "diseaseRare",
                "diseaseSevere",
                "vaccEff",
                "vaccDanger",
                "medSkept",
                "vaccIntent", 
                "parExpert",
                "immCap",
                "immSympt",
                "immWeak",
                "vaccStrain",
                "vaccTox",
                "overParenting")

# df_hist <- df_scales[,scale_vars]
plt.hist <- ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
    geom_histogram(bins = 14) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

@@

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_scales)[73:87,1:72],
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

```{r}
df_long <- df_scales
df_long$y_val <- df_long$vaccIntent
df_long <- reshape(df_long, idvar="workerId", timevar = "item", direction="long", 
             varying=list(x_val = scale_vars[-8]),
             v.names = c("x_val"))
df_long$item <- factor(df_long$item,
                       levels = seq(1,14,1),
                       labels=scale_vars[-8])

@@

ggsave("scale_scatter.png",plt.scatter)
```

>>>>

---
title: "Vaccines: Many Beliefs Pilot 4"
author: "Derek Powell"
date: "June 30, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

@@

filename <- "data/vb_pilot4.csv"

@@

df <- df[ , -which(names(df) %in% remove_cols)]
df <- df[which(df$vaccDanger_check_3==3 & df$hb_check_5==5),]
```

```{r}
all_items <- c("hb_1",
"hb_2",
"hb_3",
"hb_4",
"nat_1",
"nat_2r",
"nat_3",
"nat_4",
"nat_5r",
"medSkept_1",
"medSkept_2r",
"medSkept_3",
"medSkept_4",
"medSkept_5r",
"diseaseRare_1",
"diseaseRare_2",
"diseaseRare_3r",
"diseaseRare_4",
"diseaseRare_5r",
"diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3r",
"diseaseSevere_4",
"diseaseSevere_5r",
"vaccEff_1",
"vaccEff_2r",
"vaccEff_3r",
"vaccEff_4",
"vaccDanger_1",
"vaccDanger_2r",
"vaccDanger_3",
"vaccDanger_4r",
"vaccTox_1r",
"vaccTox_2",
"vaccTox_3",
"vaccTox_4r",
"vaccStrain_1",
"vaccStrain_2r",
"vaccStrain_3",
"vaccStrain_4r",
"vaccStrain_5",
"vaccIntent_1r",
"vaccIntent_2",
"vaccIntent_3r",
"vaccIntent_4",
"vaccIntent_5r",
"parentExpert_1",
"parentExpert_2",
"parentExpert_3",
"parentExpert_4r",
"parentExpert_5r",
"infantImmLimCap_1",
"infantImmLimCap_2r",
"infantImmLimCap_3",
"infantImmLimCap_4",
"infantImmLimCap_5r",
"infantImmWeak_1",
"infantImmWeak_2",
"infantImmWeak_3",
"infantImmWeak_4r",
"infantImmWeak_5r",
"overpar_1r",
"overpar_2",
"overpar_3",
"overpar_4",
"overpar_5r",
"overpar_6r")

@@

```{r}
library(ggplot2)
# df <- read.csv("vb_pilot2.csv")

@@

This is a notebook for the fourth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 1 to comprehension checks, leaving 99.

@@

Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters.

@@

# Problem scales

@@

Disease severe is now a weaker scale. I'd wager this is due to our changes, as this used to be highly reliable at $\alpha$  = .86.

```{r}
diseaseSevere <- all_items[20:24]

### Diagnosing

ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
corrplot(cor(df[,diseaseSevere]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

This scale took a hit -- possibly due to the reverse coding? possibly just random variation. It went down from .825 so random variation is possible but seems on the extreme end.

```{r}
nat <- all_items[5:9]

naturalism.alpha <- psych::alpha(df[,nat])
naturalism.alpha$total$raw_alpha
naturalism.alpha

This got worse!

```{r}
# overPar <- all_items[62:67]
overPar <- c(
"overpar_2",
"overpar_3",
"overpar_4",
"overpar_5r")

### Diagnosing

No clear fixes here, just not doing very well.

# Acceptable scales

The remaining scales are (within rounding) in the acceptable reliabiltiy range.

@@

This reliability is lower but this scale is unchanged (and a pre-existing scale, so we should leave it alone).

```{r}
hb <- all_items[1:4]

@@

@@

```{r}
diseaseRare <- all_items[15:19]

@@

@@

```{r}
vaccEff <- all_items[25:28]

@@

```{r}
vaccDanger <- all_items[29:32]

@@

```{r}
vaccTox <- all_items[33:36]

@@

This is just barely making the grade now. Removing 5r would improve the reliability. I thought the phrasing of that item was a bit awkward after reverse coding, so maybe it can be fixed.

```{r}
medSkept <- all_items[10:14]

medSkept.alpha <- psych::alpha(df[,medSkept])
medSkept.alpha$total$raw_alpha
medSkept.alpha

corrplot(cor(df[,medSkept]),
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

@@

```{r}
vaccIntent <- all_items[42:46]

@@

Success! Reliability is very solid.

```{r}
parExpert <- all_items[47:51]

parExpert.alpha <- psych::alpha(df[,parExpert])
parExpert.alpha$total$raw_alpha
parExpert.alpha
```

Looks a little two-dimensional though. Items 4 and 5 are both about trusing doctors' advice, so I suppose it's not surprising they hang together even more strongly.

@@

Reliability is now very good.

```{r}
immCap <- all_items[52:56]

@@

@@

Looks good!

```{r}
immWeak <- all_items[57:61]

@@

```{r}
vaccStrain <- all_items[37:41]

@@

@@

```{r}
df_scales<-df_main
df_scales$holBalance <- rowMeans(df[,hb])
df_scales$naturalism <- rowMeans(df[,nat])
df_scales$diseaseRare <- rowMeans(df[,diseaseRare])
df_scales$diseaseSevere <- rowMeans(df[,diseaseSevere])
df_scales$vaccEff <- rowMeans(df[,vaccEff])
df_scales$vaccDanger <- rowMeans(df[,vaccDanger])
df_scales$medSkept <- rowMeans(df[,medSkept])
df_scales$vaccIntent <- rowMeans(df[,vaccIntent])
# df_scales$parDuty <- rowMeans(df[,parDuty])
df_scales$parExpert <- rowMeans(df[,parExpert])
df_scales$immCap <- rowMeans(df[,immCap])
# df_scales$immSympt <- rowMeans(df[,immSympt])
df_scales$immWeak <- rowMeans(df[,immWeak])
df_scales$vaccStrain <- rowMeans(df[,vaccStrain])
df_scales$vaccTox <- rowMeans(df[,vaccTox])
df_scales$overParenting <- rowMeans(df[,overPar])
```

@@

scale_vars <- c("holBalance",
                "naturalism",
                "diseaseRare",
                "diseaseSevere",
                "vaccEff",
                "vaccDanger",
                "medSkept",
                "vaccIntent", 
                "parExpert",
                "immCap",
                "immWeak",
                "vaccStrain",
                "vaccTox",
                "overParenting")

# df_hist <- df_scales[,scale_vars]
plt.hist <- ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
    geom_histogram(bins = 14) + facet_wrap(~variable) + xlim(1,7)

@@

```{r}
df_long <- df_scales
df_long$y_val <- df_long$vaccIntent
df_long <- reshape(df_long, idvar="workerId", timevar = "item", direction="long", 
             varying=list(x_val = scale_vars[-8]),
             v.names = c("x_val"))
df_long$item <- factor(df_long$item,
                       levels = seq(1,13,1),
                       labels=scale_vars[-8])

@@

# ggsave("scale_scatter.png",plt.scatter)
plt.scatter
```

# Coefficient $\omega$ reliability

Coefficient $\alpha$ has a number of well-known problems, not the least of which it is often biased (either under or over-estimating). Most people who know now recommend the use of coeffiicent $\omega$, because it is unbiased and also readily interpretable: $\omega$ represents the proportion of variance in scale scores accounted for by the latent factor.

Here I'm calculating robust $\omega$ using the coefficientalpha package. A (non-robust?) implementation is also available in the psych package that relies on an SEM package.

If $\omega$ is to be trusted it looks like the bias in $\alpha$ is leading to an underestimate of the reliability of most scales.

```{r}
coefficientalpha::omega(df[,nat])
```

## DiseaseSeverity

```{r}
coefficientalpha::omega(df[,diseaseSevere])
```

## Over-parenting

Still poor.

```{r}
coefficientalpha::omega(df[,overPar])
```

## Medical skepticism

```{r}
coefficientalpha::omega(df[,medSkept])
```

```{r}
coefficientalpha::omega(df[,diseaseRare])
```

### 2018-09-18 pilots/pilot5/vacc_manyBelief_pilot5.Rmd
added files

---
title: "Vaccines: Many Beliefs Pilot 4"
author: "Derek Powell"
date: "June 30, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

@@

filename <- "data/vb_pilot4.csv"

@@

```{r}
all_items <- c("hb_1",
"hb_2",
"hb_3",
"hb_4",
"nat_1",
"nat_2r",
"nat_3",
"nat_4",
"nat_5r",
"medSkept_1",
"medSkept_2r",
"medSkept_3",
"medSkept_4",
"medSkept_5r",
"diseaseRare_1",
"diseaseRare_2",
"diseaseRare_3r",
"diseaseRare_4",
"diseaseRare_5r",
"diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3r",
"diseaseSevere_4",
"diseaseSevere_5r",
"vaccEff_1",
"vaccEff_2r",
"vaccEff_3r",
"vaccEff_4",
"vaccDanger_1",
"vaccDanger_2r",
"vaccDanger_3",
"vaccDanger_4r",
"vaccTox_1r",
"vaccTox_2",
"vaccTox_3",
"vaccTox_4r",
"vaccStrain_1",
"vaccStrain_2r",
"vaccStrain_3",
"vaccStrain_4r",
"vaccStrain_5",
"vaccIntent_1r",
"vaccIntent_2",
"vaccIntent_3r",
"vaccIntent_4",
"vaccIntent_5r",
"parentExpert_1",
"parentExpert_2",
"parentExpert_3",
"parentExpert_4r",
"parentExpert_5r",
"infantImmLimCap_1",
"infantImmLimCap_2r",
"infantImmLimCap_3",
"infantImmLimCap_4",
"infantImmLimCap_5r",
"infantImmWeak_1",
"infantImmWeak_2",
"infantImmWeak_3",
"infantImmWeak_4r",
"infantImmWeak_5r",
"overpar_1r",
"overpar_2",
"overpar_3",
"overpar_4",
"overpar_5r",
"overpar_6r")

@@

This is a notebook for the fourth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 1 to comprehension checks, leaving 99.

@@

Disease severe is now a weaker scale. I'd wager this is due to our changes, as this used to be highly reliable at $\alpha$  = .86.

```{r}
diseaseSevere <- all_items[20:24]

@@

This scale took a hit -- possibly due to the reverse coding? possibly just random variation. It went down from .825 so random variation is possible but seems on the extreme end.

```{r}
nat <- all_items[5:9]

@@

This got worse!

```{r}
# overPar <- all_items[62:67]
overPar <- c(
"overpar_2",
"overpar_3",
"overpar_4",
"overpar_5r")

@@

No clear fixes here, just not doing very well.

@@

This reliability is lower but this scale is unchanged (and a pre-existing scale, so we should leave it alone).

@@

```{r}
diseaseRare <- all_items[15:19]

@@

```{r}
vaccEff <- all_items[25:28]

@@

```{r}
vaccDanger <- all_items[29:32]

@@

```{r}
vaccTox <- all_items[33:36]

@@

This is just barely making the grade now. Removing 5r would improve the reliability. I thought the phrasing of that item was a bit awkward after reverse coding, so maybe it can be fixed.

```{r}
medSkept <- all_items[10:14]

@@

```{r}
vaccIntent <- all_items[42:46]

@@

```{r}
parExpert <- all_items[47:51]

@@

```{r}
immCap <- all_items[52:56]

@@

```{r}
immWeak <- all_items[57:61]

@@

```{r}
vaccStrain <- all_items[37:41]

@@

```{r}
coefficientalpha::omega(df[,diseaseSevere])
```

@@

Still poor.

@@

>>>>

---
title: "Vaccines: Many Beliefs Pilot 5"
author: "Derek Powell"
date: "July 14, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

@@

filename <- "data/vb_pilot5.csv"

@@

```{r}
all_items <- c("hb_1",
"hb_2",
"hb_3",
"hb_4",
"nat_1",
"nat_2r",
"nat_3",
"nat_4",
"nat_5",
"nat_6r",
"medSkept_1",
"medSkept_2r",
"medSkept_3",
"medSkept_4",
"medSkept_5r",
"medSkept_6r",
"diseaseRare_1",
"diseaseRare_2",
"diseaseRare_3r",
"diseaseRare_4",
"diseaseRare_5r",
"diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3r",
"diseaseSevere_4",
"diseaseSevere_5r",
"diseaseSevere_6",
"vaccEff_1",
"vaccEff_2r",
"vaccEff_3r",
"vaccEff_4",
"vaccDanger_1",
"vaccDanger_2r",
"vaccDanger_3",
"vaccDanger_4r",
"vaccTox_1r",
"vaccTox_2",
"vaccTox_3",
"vaccTox_4r",
"vaccStrain_1",
"vaccStrain_2r",
"vaccStrain_3",
"vaccStrain_4r",
"vaccStrain_5",
"vaccIntent_1r",
"vaccIntent_2",
"vaccIntent_3r",
"vaccIntent_4",
"vaccIntent_5r",
"parentExpert_1",
"parentExpert_2",
"parentExpert_3",
"parentExpert_4r",
"parentExpert_5r",
"infantImmLimCap_1",
"infantImmLimCap_2r",
"infantImmLimCap_3",
"infantImmLimCap_4",
"infantImmLimCap_5r",
"infantImmWeak_1",
"infantImmWeak_2",
"infantImmWeak_3",
"infantImmWeak_4r",
"infantImmWeak_5r",
"overpar_1",
"overpar_2",
"overpar_3",
"overpar_4r",
"overpar_5r")

@@

This is a notebook for the fifth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 4 to comprehension checks, leaving 96.

@@

Our changes to disease severity did not help at all and in fact hurt the reliability of the scale even with an additional item. I think we really need to iron out the issues in this scale, whether that means returning to the original or making new changes.

```{r}
diseaseSevere <- all_items[22:27]
diseaseSevere <- c("diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3r",
"diseaseSevere_4",
"diseaseSevere_5r",
"diseaseSevere_6")

@@

This scale improved very slightly, looks like we can remove either 5 or 6r and retain an alpha of .78. Since removing 6r makes this basically the original scale I think we can say that the difference between that score (.78) and the .825 it scored earlier is essentially just noise. As a spoiler, I looked at the consistency in the alpha scores for the unchanged scales (n=10) across pilot 4 and 5. The average absolute difference was .021 and the SD of the differences was .025. So I guess that makes me less interested in reading into changes or differences smaller than those values, and we should only really be struck by changes greater than .049 or so.

```{r}
nat <- all_items[5:10]

@@

This improved considerably, though it's still a tad low. Looks like item 4r is weak.

```{r}
overPar <- all_items[65:69]

@@

Items 3 and 4r really don't correlate.

@@

In pilot 4 the reliability of this was just below threshold, here it's just above.

@@

```{r}
diseaseRare <- all_items[17:21]

@@

```{r}
vaccEff <- all_items[28:31]

@@

```{r}
vaccDanger <- all_items[32:35]

@@

```{r}
vaccTox <- all_items[36:39]

@@

This is just making the grade now and looks like we are safe to remove 5r without harming reliability, though I think it's kind of an important part of the idea. So maybe we are left to choose between a 5 item scale and a scale with that item included.

```{r}
medSkept <- all_items[11:16]

@@

```{r}
vaccIntent <- all_items[45:49]

@@

```{r}
parExpert <- all_items[50:54]

@@

```{r}
immCap <- all_items[55:59]

@@

```{r}
immWeak <- all_items[60:64]

@@

```{r}
vaccStrain <- all_items[40:44]

@@

Still doesn't make the grade according to omega
```{r}
coefficientalpha::omega(df[,diseaseSevere])
```

@@

Makes the grade according to omega

@@

# Comparing studies

As mentioned in the naturalism scale section, I looked at the consistency in the alpha scores for the unchanged scales (n=10) across pilot 4 and 5. The average absolute difference was .021 and the SD of the differences was .025. So I guess that makes me less interested in reading into changes or differences smaller than those values, and we should only really be struck by changes greater than .049 or so. The alpha values correlate at *r* = .89 across studies.
